\renewcommand{\bibname}{}
\patchcmd{\thebibliography}{\chapter*}{\section*}{}{}

\begin{thebibliography}{100} 

\bibitem{reactOreilly} Banks, A., & Porcello, E. (2017). Learning REACT Functional Web Development with REACT and Redux. O’Reilly.

\bibitem{scss} Coyier, C. (2013). SASS FOR WEB DESIGNERS. https://abookapart.com/products/sass-for-web-designers

\bibitem{html} Danny Goodman. (1998). Dynamic HTML The Definitive Reference. 101 Morris Street, Sebastopol, CA 95472: O'REILLY.

\bibitem{frontEnd} Fu, C. (2016). Exploration of Web front-end development technology and optimization direction.

\bibitem{} Gaikovina Kula, R., Ouni, A., M. German, D., & Inoue, K. (2017, septiembre). On the Impact of Micro-Packages: An Empirical Study of the npm JAVASCRIPT Ecosystem. Osaka University, Japan. https://arxiv.org/abs/1709.04638

\bibitem{webPack} Gallegos, G. (2017, 20 octubre). Para que es Webpack? Medium. https://medium.com/tecninja/porque-usar-webpack-4a5004094455

\bibitem{CRA} Getting Started | Create React App. (s. f.). Create React App. https://create-react-app.dev/docs/getting-started/

\bibitem{jest} Getting Started · Jest. (s. f.). Jest. https://jest-bot.github.io/jest/docs/getting-started.html

\bibitem{} Hudson, P. (2016). Hacking with REACT [Libro electrónico]. http://www.hackingwithREACT.com/

\bibitem{javascript} JAVASCRIPT. (2020, 11 agosto). Documentación web de MDN. https://developer.mozilla.org/es/docs/Web/JAVASCRIPT

\bibitem{} K. White, S. (2020, 10 enero). The 10 most in-demand tech jobs for 2020 — and how to hire for them. CIO. https://www.cio.com/article/3235944/hiring-the-most-in-demand-tech-jobs-for-2018.html

\bibitem{mobileFirst} Mobile-first indexing best practices. (s. f.). Google Developers. https://developers.google.com/search/mobile-sites/mobile-first-indexing


\bibitem{} Open Source Initiative. (2006). The MIT license. 2015b.[Online]. Available: https://opensource. org/licenses/MIT.[Accessed 27 March 2017].


\bibitem{newTech} Popoter Pérez, G. J. (2016). Rediseño de aplicaciones utilizando las tecnologías modernas para el desarrollo web en su parte Front-end.


\bibitem{} Pozas, J. L. B. (2018, 11 enero). Las 10 profesiones de TI con mayor demanda en 2017. CIO MX. https://cio.com.mx/las-10-profesiones-ti-mayor-demanda-en-2017/

\bibitem{} ¿Qué es el open source? (2020). Red Hat. https://www.redhat.com/es/topics/open-source/what-is-open-source

\bibitem{react} REACT – A JAVASCRIPT library for building user interfaces. (s. f.). REACT. https://REACTjs.org

\bibitem{work} Riquelme, R. (2016, 17 octubre). Los 10 mejores trabajos en TI e Ingeniería. El Economista. https://www.eleconomista.com.mx/tecnologia/Los-10-mejores-trabajos-en-TI-e-Ingenieria-20161017-0053.html

\bibitem{publish} Rodriguez, M. A. (2019, 3 diciembre). Crear y publicar un paquete NPM en 4 sencillos pasos. Medium. https://medium.com/200-response/crear-y-publicar-un-paquete-npm-en-4-sencillos-pasos-8e7498b558a2

\bibitem{frontEnd2} Ruiz Inoue, K. (2020, 20 agosto). ¿Qué es el Desarrollo Front end, Back end y Fullstack? Medium. https://medium.com/deuk/qué-es-el-desarrollo-front-end-back-end-y-fullstack-2941b51afd1

\bibitem{stackOverflow} Stack Overflow Developer Survey 2020. (2020). Stack Overflow. https://insights.stackoverflow.com/survey/2020#overview

\bibitem{openSource} The Linux Foundation. (2018). Enterprise Open Source: A Practical Introduction [Libro electrónico].https://www.linuxfoundation.org/press-release/2018/08/free-ebook-enterprise-open-source-a-practical-introduction-teaches-enterprises-how-to-accelerate-open-source-efforts/

\bibitem{npm} What is npm. (2020). w3schools. https://www.w3schools.com/whatis/whatis_npm.asp

\bibitem{babel} What is Babel? · Babel. (2020). Babel. https://babeljs.io/docs/en/

\bibitem{airbnb} Agrawal, K. (2019, May 4). Airbnb Javascript style guide — Key takeaways - Docon. Medium. https://medium.com/docon/airbnb-javascript-style-guide-key-takeaways-ffd0370c053



\end{thebibliography}